Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-12 ms.tex
Fig 1, Table 6, more discussion text

\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
Earth-like Insolation?}

@@

\email{btm@astro.caltech.edu}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
\altaffiltext{\texas} {Department of Astronomy, The University of Texas at
                            Austin, Austin, TX 78712, USA}
\altaffiltext{\hjs} {Harlan J. Smith Fellow, The University of Texas at Austin}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties.
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}.
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
These data are reported in Table 1.

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we used the publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for stellar model grids.  
This software does trilinear interpolation in mass--age--\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table
\ref{Table:BGstars}.

%Table:BGstars
% Primary    RA Dec Separation DeltaR         MaxDepth
% 201295312  &  &   &          & 7.10 \pm 0.10 & 0.75
% 201465501  &  &   &          & 7.90 \pm 0.25 & 0.36
% 201546283  &  &   &          & 5.87 \pm 0.06 & 2.31
% 201779067  &  &   &          & 4.21 \pm 0.03 & 10.56

In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

@@

As stated in \textsection\ref{sec:stellarparams}, we place a distance upper limit of 500 pc 
for all stars in our sample. 
Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
contamination rate by halo giants. 
However, there are a few stars that are possibly miscategorized giants.
EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
as a target with $\logg = 3.18$, consistent with that of a giant star.
It is therefore perhaps not surprising that this system is flagged as a false positive based on 
the transit shape.
EPIC 201929294 has a reduced proper motion consistent with that of a giant star

@@

\include{table_planets}
\turnpage
\include{table_fpp}

>>>>

\title{Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
Earth-like Insolation}

@@

\email{btm@astro.caltech.edu}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
\altaffiltext{\texas} {Department of Astronomy, The University of Texas at
                            Austin, Austin, TX 78712, USA}
\altaffiltext{\hjs} {Harlan J. Smith Fellow, The University of Texas at Austin}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties.
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}.
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
These data are reported in Table 1, and a color-color diagram showing the
$r-J, J-K$ colors of our candidates is included as Fig. \ref{fig:photometry}.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{f1}}
\caption{Color-color diagram displaying $r-J, J-K$ photometry for targets 
observed by \kep\ during the original
mission (black), with our \KT\ \Ci\ planet candidates overlaid (fuchsia). 
Also included is the location of the Sun (yellow). 
Nearly all of our candidates have photometry consistent with later spectral
types than G2.}
\label{fig:photometry}
\end{figure}

\subsection{Stellar Models}
\label{sec:stellarparams}
To convert the observed photometric data into physical properties for each
star, we used the publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for stellar model grids.  
This software does trilinear interpolation in mass--age--\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table
6.

In Table 6, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

@@

As stated in \textsection\ref{sec:stellarparams}, we infer stellar parameters using the 
Dartmouth models, with a mass upper limit of $3.7 M_\odot$. 
Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
contamination rate by halo giants. 
However, there are a few stars that are possibly miscategorized giants.
EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
as a target with $\logg = 3.18$, consistent with that of a giant star.
It is therefore perhaps not surprising that this system is flagged as a false positive based on 
the transit shape.
EPIC 201929294, with a proper motion of $0.010\arcsec$ yr$^{-1}$ \citep{Zacharias12}  has 
a reduced proper motion consistent with that of a giant star.
While suggestive, this observation does not definitively provide information about the
nature of this target. 
Likewise, our false positive analysis is neither able to confirm nor exclude the planetary
nature of the observed transit signal around this target.

@@

\include{table_planets}
\begin{turnpage}
\include{table_fpp}
\end{turnpage}

\include{table_bg}
